\chapter{Requirements}
In the first part of the chapter we focus on the requirements for the wholesome application solution and related business requirements. In the second part we specify the technical point of view.

\section{Business requirements}
Our goal is to define and formalize the process of ordering the taxi in the company. Based on the results we create the API which allows the clients go through this process. 

Second goal is to design the scheduling system which distribute the orders between the drivers automatically. The main goal for the scheduler is to provide the customer detailed information during the order process and minimize the waiting time for the taxi. After the first estimation system should change the estimations as little as possible. Scheduler must support processing the orders with specified time of pick-up. The most important is to assure that the driver arrives precisely on time in this case.

\section{Technical requirements}
	Our first requirement is to have the back-end and front-end strictly separated. This allows us in the future having more different clients which can be connected to our logic. With this architecture we can easily integrate ordering system into common applications like Facebook Messenger or Slack and do not relay on custom application only.
	
	Our API must be well-documented and easy to use so the front-end part can relay on the information in documentation. The communication with API must be encrypted - we should use the HTTPS protocol. 
	
	Because we have other developers working on the front-end side, we should keep the installation process of the back-end as simple as possible. We should be able to run it on various operating systems - specifically latest version of Windows, Ubuntu and MacOS X.
	
	The stack we use for back-end application should be also prepared for scaling in the future and keep the downtime during the deployment at minimum.


\todo{Poznámky, které smažu}
\begin{itemize}
	\item  it is very easy to order via phone call make it as easy as possible
	\item Customers must have overview how much their order will approximetly cost and must be able to select their driver. Also they must have approximate estimate when their taxi will come.
	\item Customers should be informed about their ordered driver status - where he is and when them will come
	\item better customer service - remember name, favorite location, other things
	\item security - strong competition, already few cases of hacking and data stealing
	\item some of the things written tailored for our local taxi company but should be easily rewritten and reused for some other company with different requirements and priorities
	\item authorization
	\item two main types of orders - scheduled on time and normal. Our high priority is to be there for scheduled precisely on time.
	\item handling frauds
	\item collect as much data for orders as possible for later improvements
\end{itemize}